Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-06 manuscript/manuscript.Rmd
Finished simulation section.

Figure *insert* shows bi-modal distributions, and their respective p-values using the empirical goodness of fit test.

```{r goodness-of-fit-3, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0("Bi-modal distributions and empirical goodness of fit test results.")

>>>>

In figure *insert* we apply the empirical goodness of fit test to assess central normality of features that are composed of a mixture of samples drawn from two normal distributions. With increased separation of the underlying normal distributions, the probability of the feature being centrally normal decreases, as expected.

```{r goodness-of-fit-3, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Bi-modal distributions and empirical goodness of fit test results. ",
  "The feature (black) is a mixture of two identical sample sets (blue and orange) ",
  "drawn from normal distributions that are offset by a distance $d$. ",
  "We use the empirical goodness of fit test to compute p-values for the hypothesis that ",
  "the distribution is centrally normal. As may be observed, with increasing offset $d$ ",
  "the probability that the feature is centrally normal decreases. ",
  "Quantile-quantile plots are drawn below each distribution."
)
